\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2018-01-16 eg6-letters/NIM/review-1/review-1.tex
Minor fix to compile NIM review

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\
Regarding the electric field it is unclear what you call the induction gap. We
provide these fields for the drift region and the inter-GEM regions which we 
find most relevant. If extra information is needed, please let us know.\\}
The gain of such triple GEM configuration has been studied by 
CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
the lack of calibration of some electronics elements makes it impossible for 
us to extract a gain specific to the GEM system at this point.}

>>>>

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target and the RTPC with respect to CLAS sectrometer.\\
Regarding the electric field it is unclear what you call the induction gap. We
provide these fields for the drift region and the inter-GEM regions which we 
find most relevant. If extra information is needed, please let us know.\\
The gain of such triple GEM configuration has been studied by 
CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
the lack of calibration of some electronics elements makes it impossible for 
us to extract a gain specific to the GEM system at this point.}
